Supporting information: Copulas and their potential for ecology

### 2019-10-03 Paper.Rmd
figure fixed within a page: downsized

```{r tab_stat_npa_asym_simple,echo=F,results="markup"}
library(kableExtra)

tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.5.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}

@@

<!--Plots for AR(1) with Clayton-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u-D2l_vs_Kendall's Tau.pdf} \\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption{Comparison of correlation and tail association statistics between 
environmental-noise inputs and ecological-variable 
outputs, AR(1) model, Clayton copula. Red and blue points give 
means over 50 replicate simulations of the listed statistics, 
red points are for noise inputs and blue points are for
model outputs. Error bars are standard errors. 
$P$-values (purple points, right axis) are for a 
paired $t$-test of the null hypothesis that the distributions have the same mean. 
For bottom panels, headers give Pearson correlations for
the points. The regression line through the points (black) was similar
to the 1-1 line (green). 
See methods section for Q2 
for details.\label{fig_Cause4copula_C_kend_ar1}}
\end{center}
\end{figure}
<!--***DAN: Shyamolina, the panels in the bottom row do not line up with the others. 
I remember you fixed this before for the sup mat figs, can you plase fix it again here?
Also, can you make the panels smaller or more tightly packed or soemthing
so the whole figure plus caption fits on a page?-->

>>>>

```{r tab_stat_npa_asym_simple,echo=F,results="markup"}
library(kableExtra)
source("./make_table_stat_fn.R")
tab_asym<-readRDS("./Results/asym_sens_results/stat_npa_asym_b_0.1_b_0.5.RDS")
tab_stat_npa_asym<-c()
for(i in c(1:8)){
  temp<-make_table_stat_fn(data=tab_asym[[i]])
  tab_stat_npa_asym<-rbind(tab_stat_npa_asym,temp)
}

@@

<!--Plots for AR(1) with Clayton-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\vspace{-0.2 cm}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\vspace{-0.2 cm}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\vspace{-0.2 cm}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u-D2l_vs_Kendall's Tau.pdf} \\
\hspace{-0.6 cm}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=4.3 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption{Comparison of correlation and tail association statistics between 
environmental-noise inputs and ecological-variable 
outputs, AR(1) model, Clayton copula. Red and blue points give 
means over 50 replicate simulations of the listed statistics, 
red points are for noise inputs and blue points are for
model outputs. Error bars are standard errors. 
$P$-values (purple points, right axis) are for a 
paired $t$-test of the null hypothesis that the distributions have the same mean. 
For bottom panels, headers give Pearson correlations for
the points. The regression line through the points (black) was similar
to the 1-1 line (green). 
See methods section for Q2 
for details.\label{fig_Cause4copula_C_kend_ar1}}
\end{center}
\end{figure}
<!--***DAN: Shyamolina, the panels in the bottom row do not line up with the others. 
I remember you fixed this before for the sup mat figs, can you plase fix it again here?
Also, can you make the panels smaller or more tightly packed or soemthing
so the whole figure plus caption fits on a page?
***Shya: Ok, now I fixed it. See the margin specifications are different for Paper and Suuppmat, 
that's why I have to downsize the figure here in the maintext.-->

### 2019-10-03 SupportingInformation.Rmd
figure fixed within a page: downsized

<!--Function to generate a table for npa results-summary with bivariate data, this one about asymmetry of tail dependence-->
```{r make_table_stat_fn, echo=F}
fractxt<-function(fracval,numsurrog){
  ptxt<-''
  if (fracval>.5*numsurrog){                        
    ptxt<-paste(">",fracval,sep='')
  } 
  if (fracval<=.5*numsurrog){
    ptxt<-paste("<",numsurrog-fracval,sep='')
  }
  return(ptxt)
}

make_table_stat_fn<-function(data){

  #atdres<-data.frame(Statistic=c("$\\cor_{0,0.1}-\\cor_{0.9,1}$",
  #                               "$\\Ps_{0,0.1}-\\Ps_{0.9,1}$",
  #                               "$\\Dsq_{0.9,1}-\\Dsq_{0,0.1}$"),
  atdres<-data.frame(Statistic=c("cor$_{FS}$-cor$_{LS}$",
                                 "P$_{FS}$-P$_{LS}$",
                                 "D$_{LS}^2$-D$_{FS}^2$"),
                     Kendall=rep("",3),
                     Spearman=rep("",3),stringsAsFactors = F)

  atdres[1,2]<-fractxt(data$corlmcoru_frac_K,numsurrog = data$numsurrog_success_K)
  atdres[1,3]<-fractxt(data$corlmcoru_frac_S,numsurrog = data$numsurrog_success_S)
  atdres[2,2]<-fractxt(data$PlmPu_frac_K,numsurrog = data$numsurrog_success_K)
  atdres[2,3]<-fractxt(data$PlmPu_frac_S,numsurrog = data$numsurrog_success_S)
  atdres[3,2]<-fractxt(data$D2umD2l_frac_K,numsurrog = data$numsurrog_success_K)
  atdres[3,3]<-fractxt(data$D2umD2l_frac_S,numsurrog = data$numsurrog_success_S)

  return(atdres)

}
```

>>>>

<!--Sourcing Function to generate a table for npa results-summary with bivariate data, this one about asymmetry of tail dependence-->
```{r source_make_table_stat_fn, echo=F}
source("./make_table_stat_fn.R")
```
